WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-05-31 article/Article.tex
some additions to the article
darcs-hash:20060531220421-2fc9d-6234444c19f99cec34461229ea33730c1797483a.gz

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$}{\small{,}} Zachary Pincus{$^2$} {\small{and}} Benoit Regrain{$^3$}}
\authoraddress{{$^1$}Unit\'e de Biologie du D\'eveloppement et de la Reproduction, Institut National de la Recherche Agronomique, 78350 Jouy-en-Josas, France\\
{$^2$}Program in Biomedical Informatics and Department of Biochemistry, Stanford University School of Medicine, Stanford, California\\
{$^3$}CREATIS, CNRS UMR 5515, 69621 Villeurbanne, France}

@@

@@

Several tests are available\footnote{There is currently 49 tests with the default
configuration.} for Python, Tcl and Java. They can be run with the \verb$ctest$
command.

@@

WrapITK will work properly with the ITK 2.6.0 release.

@@

@@

Java \cite{JavaWebSite} is required only to build java support.
WrapITK have been tested with java \verb$1.5.0_06-b05$.

@@

This media also contain several packages which may be useful to use WrapITK,
and which are not available in mandriva linux 2006.0. Here is the full list:
\begin{itemize}
  \item \verb$cmake$
  \item \verb$itk-data$
  \item \verb$itk-doc$
  \item \verb$itk-examples$
  \item \verb$itkvtk-devel$
  \item \verb$libitk$
  \item \verb$libitk-devel$
  \item \verb$libvtk$
  \item \verb$libvtk-devel$
  \item \verb$libvtk-qt$
  \item \verb$python-itk$
  \item \verb$python-itk-numarray$
  \item \verb$python-itkvtk$
  \item \verb$python-vtk$
  \item \verb$tcl-itk$
  \item \verb$tcl-vtk$
  \item \verb$vtk-data$
  \item \verb$vtk-doc$
  \item \verb$vtk-examples$
  \item \verb$vtk-test-suite$
  \item \verb$wrapitk-devel$
\end{itemize}

@@

On linux boxes however, the user have to set the \verb$LD_LIBRARY_PATH$ to
point to libSwigRuntime.so. For example
\verb$export LD_LIBRARY_PATH=/usr/lib/InsightToolkit/WrapITK/Python-SWIG$.

@@

Lots of classes have a \verb$New()$ method which returns a smart pointer to that class. The
\verb$New()$ method in python has some additional features:
\begin{itemize}
  \item Arguments to the new method are assumed to be filter inputs. So you could
write:
\begin{verbatim}
adder = itk.AddImageFilter[...].New()
adder.SetInput1( readerA.GetOutput() )
adder.SetInput2( readerB.GetOutput() )
\end{verbatim}
or you could write
\begin{verbatim}
adder = itk.AddImageFilter[...].New( readerA.GetOutput(), readerB.GetOutput() )
\end{verbatim}
or even
\begin{verbatim}
adder = itk.AddImageFilter[...].New( readerA, readerB )
\end{verbatim}
In that case, \verb$New$ will use the \verb$GetOutput()$ method of the object, if it
exist, to get the image and set the inputs of the new filter.

@@

\verb$itk$ module can be very long to import. The \verb$itkConfig$ module define
a \verb$ImportCallback$ method which will be called when each sub module is
imported in the import process. \verb$ImportCallback$ can be customized to report the
progress status of the import process. It must be a function that can take
the name of the library being imported as a parameter. Here is an example of a very
basic callback function which display the name of the submodule being imported on
the standard error output.
\small \begin{verbatim}
import sys, itkConfig
def stderr_callback(name, progress):
  if progress == 0:
    print >> sys.stderr, "Loading %s..." % name,
  if progress == 1:
    print >> sys.stderr, "done"
itkConfig.ImportCallback = stderr_callback
import itk
\end{verbatim} \normalsize

@@

@@

@@

@@

  \item \verb$WRAP_IMAGE_FILTER_type(size)$ . \verb$type$ can be one of:
  \begin{itemize}
    \item \verb$USIGN_INT$
    \item \verb$SIGN_INT$
    \item \verb$INT$
    \item \verb$REAL$
    \item \verb$VECTOR_REAL$
    \item \verb$COV_VECTOR_REAL$
    \item \verb$RGB$
    \item \verb$ALL$
    \item \verb$SCALAR$
    \item \verb$VECTOR$
  \end{itemize}

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$}{\small{,}} Zachary Pincus{$^2$} {\small{and}} Benoit Regrain{$^3$}}
\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du D\'eveloppement et 
Reproduction, Jouy en Josas, F-78350, France\\
{$^2$}Program in Biomedical Informatics and Department of Biochemistry, Stanford University School of Medicine, Stanford, California\\
{$^3$}CREATIS, CNRS UMR 5515, 69621 Villeurbanne, France}

@@

  \item  Loading python modules can take lot of time. With WrapITK, by default,
only the modules really used are loaded, and so the loading time is higly shorter
in common situations.

@@

Several tests are available\footnote{There is currently 49 tests with the default
configuration.} for Python, Tcl and Java. They ensure the high quality of WrapITK.
They can be run with the \verb$ctest$ command.

@@

WrapITK will work properly with the ITK 2.8.0 release.

@@

Some required patch may appear in the development version version of WrapITK. Those
patches are required for the last stable version of ITK, and should be already
integrated in the last CVS version of ITK.

@@

Java \cite{JavaWebSite} is required only to build java support.
WrapITK have been tested with java \verb$1.5.0_06-b05$ and \verb$1.4.2_11$.

@@

This media also contain several packages which may be useful to use WrapITK,
and which are not available in mandriva linux 2006.0. Here is the full list:
\begin{itemize}
  \item \verb$cmake$
  \item \verb$darcs$
  \item \verb$itk-data$
  \item \verb$itk-doc$
  \item \verb$itk-examples$
  \item \verb$itkvtk-devel$
  \item \verb$libitk$
  \item \verb$libitk-devel$
  \item \verb$libvtk$
  \item \verb$libvtk-devel$
  \item \verb$libvtk-qt$
  \item \verb$python-itk$
  \item \verb$python-itk-numarray$
  \item \verb$python-itkvtk$
  \item \verb$python-vtk$
  \item \verb$tcl-itk$
  \item \verb$tcl-vtk$
  \item \verb$vtk-data$
  \item \verb$vtk-doc$
  \item \verb$vtk-examples$
  \item \verb$vtk-test-suite$
  \item \verb$wrapitk-devel$
\end{itemize}

@@

On linux boxes however, the user have to set the \verb$LD_LIBRARY_PATH$ to
point to libSwigRuntime.so. For example
\verb$export LD_LIBRARY_PATH=/usr/lib/InsightToolkit/WrapITK/Python-SWIG$.
This step is not required with the mandriva's package.

@@

Lots of classes have a \verb$New()$ method which returns a smart pointer to an object of
that class. In python, the \verb$New()$ method has some additional features:
\begin{itemize}
  \item Arguments to the new method are assumed to be filter inputs. So you could
write:
\begin{verbatim}
adder = itk.AddImageFilter[...].New()
adder.SetInput1( readerA.GetOutput() )
adder.SetInput2( readerB.GetOutput() )
\end{verbatim}
or you could write
\begin{verbatim}
adder = itk.AddImageFilter[...].New( readerA.GetOutput(), readerB.GetOutput() )
\end{verbatim}
or even
\begin{verbatim}
adder = itk.AddImageFilter[...].New( readerA, readerB )
\end{verbatim}
In that case, \verb$New()$ will use the \verb$GetOutput()$ method of the object, if it
exist, to get the image and set the inputs of the new filter.

@@

WrapITK modules can be very long to import. The \verb$itkConfig$ module define
a \verb$ImportCallback$ method which will be called when each sub module is
imported in the import process. \verb$ImportCallback$ can be customized to report the
progress status of the import process. It must be a function that can take
the name of the library being imported as a parameter. Here is an example of a very
basic callback function which display the name of the submodule being imported on
the standard error output.
\small \begin{verbatim}
import sys, itkConfig
def stderr_callback(name, progress):
  if progress == 0:
    print >> sys.stderr, "Loading %s..." % name,
  if progress == 1:
    print >> sys.stderr, "done"
itkConfig.ImportCallback = stderr_callback
import itk
\end{verbatim} \normalsize

@@

It must be noticed that using \verb$import itk$ load only python code, and doesn't load
any C++ compiled code. This feature is called {\em lazy loading}. It imply some specific
behaviors:
\begin{itemize}
 \item \verb$import itk$ is done in a very short time
 \item a compiled module is loaded only when a class in that module is used. Thus,
when a python program is run, only the revelant modules are loaded in memory
 \item using a class in a program can block the program (for a short time). The user
can choose to load the entire library at once with the command \verb$itk.force_load()$.
\end{itemize}

@@

Some examples are available in \verb$Tcl/Tests$ directory.

@@

Some examples are available in \verb$Java/Tests$ directory.

@@

  \item \verb$WRAP_IMAGE_FILTER_type(size)$ . \verb$type$ can be one of:
  \begin{itemize}
    \item \verb$USIGN_INT$ to select all the image types with unsigned integral
pixel types selected by the user
    \item \verb$SIGN_INT$ to select all the image types with signed integral
pixel types selected by the user
    \item \verb$INT$ to select all the image types with signed and unsigned integral
pixel types selected by the user
    \item \verb$REAL$ to select all the image types with real pixel types selected by the user
    \item \verb$VECTOR_REAL$ to select all the image types with \verb$Vector$
pixel types selected by the user
    \item \verb$COV_VECTOR_REAL$ to select all the image types with \verb$CovariantVector$
pixel types selected by the user
    \item \verb$RGB$ to select all the image types with \verb$RGBPixel$
pixel types selected by the user
    \item \verb$SCALAR$ to select all the image types with scalar pixel types selected by the user
    \item \verb$VECTOR$ to select all the image types with \verb$Vector$ and \verb$CovariantVector$
pixel types selected by the user
    \item \verb$ALL$ to select all the image types selected by the user.
  \end{itemize}
